Contextuality and the Born Rule in Fuzzy Quantum Theories

### 2017-03-14 prop_letter.tex
prop_letter.tex Follow "REVTEX 4.1 Author's Guide" to revise the file

\documentclass[12pt]{iopart}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{iopams}
\usepackage{setstack}

@@

\begin{document}
\letter{Contextuality and the Born Rule in Fuzzy Quantum Theories}

\author{Andrew J Hanson$^{1}$, Gerardo Ortiz$^{2}$,
Amr Sabry$^{1}$ and Yu-Tsung Tai$^{3,1}$}
\address{$^{1}$ School of Informatics and Computing, Indiana
University, Bloomington, IN 47405, USA}
\address{$^{2}$ Department of Physics, Indiana University, Bloomington, IN
47405, USA}
\address{$^{3}$ Department of Mathematics, Indiana University, Bloomington,
IN 47405, USA}
\ead{ortizg@indiana.edu}
\begin{abstract}
\today
\end{abstract}
\pacs{03.65.-w, 03.65.Ta, 02.40.Dr, 02.50.Cw, 02.50.Le}
\noindent{\it Keywords\/}: {Finite precision measurement, the Born rule, Gleason's theorem, interval-valued
probability, discrete quantum theory}

\submitto{\jpa}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Textbook quantum mechanics asserts that, given a quantum spin system
described by the wave function
$\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
and given the observable
$S_z =
\frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
then the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$
(with post-measurement state $\fket{\ps\frac{1}{2}}$) is
$\frac{\pi}{4}$ and the probability of observing the eigenvalue
$\minus\frac{\hbar}{2}$ (with post-measurement state
$\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
frequency interpretation of probability, the above assertion implies
that when performing a very large number of experiments on quantum
systems described by wave function $\ket{\psi}$, a fraction
$\frac{\pi}{4}$ of the experiments will result in the observation
$\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$ will
result in the observation $\minus\frac{\hbar}{2}$.

@@

The
Kochen-Specker theorem asserts that there is no function~$v$ assigning
a definitely value to all observables such that
\begin{equation}\eqalign{ 
v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
}\label{eq:Kochen-Specker-Rules}\end{equation}
if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
is a function~$v$ satisfying these two properties, it must send
an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

\begin{table}
\caption{\label{table:commonBasis}In each row, three observables are listed
in the left column commutes, and their common eigenbasis is listed
in the right column. In order to unified and simplify notation, we
do not normalize eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}

\begin{tabular}{ccc|cccc} 
\br 
\multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis} \\
\mr 
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ & $(1, 1, 1, 1)$ & $(1, -1, 1, -1)$ & $(1, 1, -1, -1)$ & $(1, -1, -1, 1)$ \\
$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(1, 1, 1, -1)$ & $(1, 1, -1, 1)$ & $(1, -1, 1, 1)$ & $(-1, 1, 1, 1)$ \\
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ & $(1, 0, 1, 0)$ & $(0, 1, 0, 1)$ & $(1, 0, -1, 0)$ & $(0, 1, 0, -1)$ \\
$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ & $(1, 1, 0, 0)$ & $(1, -1, 0, 0)$ & $(0, 0, 1, 1)$ & $(0, 0, 1, -1)$ \\
$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
\br 
\end{tabular} 
\end{table}
Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
if we want to reformulate the above argument in the language of quantum
probability measures, we first need to find the common eigenbasis
of each row and column, and consider the projections to each eigenvectors.
Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
The Kochen-Specker theorem could then be proved by showing there is
no function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $ satisfying
equation~(\ref{eq:Kochen-Specker-Rules}), where 
\begin{equation}
\events_{24}=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
\end{equation}
which is a sub-event space defined in definition~\ref{def:sub-event-space}.
This kind of $v$ is actually a quantum cryptodeterministic measure.
Since a cryptodeterministic measure is a special case of real-valued
probability measure, by theorem~\ref{lemma:classical-probability-measures},
the quantum cryptodeterministic measure~$v$ exists if and only if
there exists a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
which should at least satisfy
\begin{equation}\eqalign{ 
1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)
}\label{eq:Kernaghan-1}\end{equation}
because of table~\ref{table:commonBasis}. $f$ should also satisfy
the following equations since the vectors in each equation form an
orthogonal basis~\cite{Kernaghan1994,peres1995quantum}:
\begin{equation}\eqalign{ 
1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}
}\label{eq:Kernaghan-2}\end{equation}
In equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}, there
are odd number of equations, but each $f\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$
occurs twice. Therefore, there is no frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}.

@@

First, based on a Born rule probability measure, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
it is easy to construct a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
whose unique core element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.
For example, when $\mathscr{I}$ is $\left\{ \imposs,\necess,\left[\frac{1}{4},\frac{1}{4}\right],\left[\frac{1}{2},\frac{1}{2}\right],\left[\frac{3}{4},\frac{3}{4}\right]\right\} $,
we have $\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events_{24}\rightarrow\mathscr{I}$
and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
where $\iota_{\infty}\left(x\right)=\left[x,x\right]$ and $\circ$
denote function composition. This provides an example that a well-behaved
quantum IVPM exists even if $\mathscr{I}$ is discrete. Well-behaved
quantum IVPMs happen when mapping to other kind of intervals. For
example, we can add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Let 
\begin{equation} 
\iota_1(x)=\cases{ 
\necess & if $x=1$ ;\\ 
\imposs & if $x=0$ ;\\ 
\unknown & otherwise. 
}\label{eq:homomorphism-1} \end{equation}
We still have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.

@@

\begin{example}[Four-dimensional quantum real-valued probability
measure]\label{ex:four-dimensional-real-value}Consider the frame
function~$f:\mathcal{T}_{24}\rightarrow\left[0,1\right]$ again.
Apart from equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2},
$f$ should also satisfy the following equations: 
\begin{equation}\eqalign{ 
1 = f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
1 = f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
1 = f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
1 = f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
1 = f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1)+f(1,1,-1,-1)\textrm{ ,}\\ 
1 = f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0)+f(1,1,1,-1)\textrm{ ,}\\ 
1 = f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1)+f(1,1,1,-1)\textrm{ ,}\\ 
1 = f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0)+f(1,1,1,1)\textrm{ ,}\\ 
1 = f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1)+f(1,1,1,1)\textrm{ .} 
}\label{eq:non-Kernaghan}\end{equation}
\qed\end{example}

>>>>

\documentclass[reprint, aps, prl,superscriptaddress, showpacs,
showkeys]{revtex4-1} 
\let\bibhang\relax
\let\citename\relax
\let\bibfont\relax
\let\Citeauthor\relax
\let\textcite\relax
\makeatletter
\DeclareRobustCommand{\MakeUppercase}[1]{{%
      \def\i{I}\def\j{J}%
      \def\reserved@a##1##2{\let##1##2\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\uppercase{#1}}%
      \reserved@a
   }}
\DeclareRobustCommand{\MakeLowercase}[1]{{%
      \def\reserved@a##1##2{\let##2##1\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\lowercase{#1}}%
      \reserved@a
   }}
\makeatother
\expandafter\let\csname ver@natbib.sty\endcsname\relax
\renewcommand{\bibliography}[1]{}
\usepackage[ backend=biber,style=phys]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{hyperref}

@@

\begin{document}

\title{Contextuality and the Born Rule in Fuzzy Quantum Theories}

\author{Andrew J Hanson}
\affiliation{School of Informatics and Computing, Indiana University, Bloomington,
IN 47405, USA}

\author{Gerardo Ortiz}
\affiliation{Department of Physics, Indiana University, Bloomington, IN 47405,
USA}

\author{Amr Sabry}
\affiliation{School of Informatics and Computing, Indiana University, Bloomington,
IN 47405, USA}

\author{Yu-Tsung Tai}
\affiliation{Department of Mathematics, Indiana University, Bloomington, IN 47405,
USA}
\affiliation{School of Informatics and Computing, Indiana University, Bloomington,
IN 47405, USA}

\date{\today }

\pacs{03.65.-w, 03.65.Ta, 02.40.Dr, 02.50.Cw, 02.50.Le}

\keywords{Finite precision measurement, the Born rule, Gleason's
theorem, interval-valued probability, discrete quantum theory}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Textbook quantum mechanics asserts that, given a quantum spin system
described by the wave function
$\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
and given the observable
$S_z =
\frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
then the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$
(with post-measurement state $\fket{\ps\frac{1}{2}}$) is
$\frac{\pi}{4}$ and the probability of observing the eigenvalue
$\minus\frac{\hbar}{2}$ (with post-measurement state
$\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
frequency interpretation of probability, the above assertion implies
that when performing a very large number of experiments on quantum
systems described by wave function $\ket{\psi}$, a fraction
$\frac{\pi}{4}$ of the experiments will result in the observation
$\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$ will
result in the observation $\minus\frac{\hbar}{2}$.

@@

The
Kochen-Specker theorem asserts that there is no function~$v$ assigning
a definitely value to all observables such that
\begin{eqnarray}
v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
\label{eq:Kochen-Specker-Rules}\end{eqnarray}
if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
is a function~$v$ satisfying these two properties, it must send
an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

\begin{table}
\caption{\label{table:commonBasis}In each row, three observables are listed
in the left column commutes, and their common eigenbasis is listed
in the right column. In order to unified and simplify notation, we
do not normalize eigenstates, and represent the state~$\alpha_{0}\ket{0}+\alpha_{1}\ket{1}+\alpha_{2}\ket{2}+\alpha_{3}\ket{3}$
as $\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$.}
\begin{ruledtabular}
\begin{tabular}{ccc|cccc} 
\multicolumn{3}{c}{Commuting observables} & \multicolumn{4}{c}{Common eigenbasis} \\
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\mathbb{1}$ & $\sigma_{z}\otimes\sigma_{z}$ & $(1, 0, 0, 0)$ & $(0, 1, 0, 0)$ & $(0, 0, 1, 0)$ & $(0, 0, 0, 1)$ \\
$\sigma_{x}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{x}\otimes\sigma_{x}$ & $(1, 1, 1, 1)$ & $(1, -1, 1, -1)$ & $(1, 1, -1, -1)$ & $(1, -1, -1, 1)$ \\
$\sigma_{x}\otimes\sigma_{z}$ & $\sigma_{z}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(1, 1, 1, -1)$ & $(1, 1, -1, 1)$ & $(1, -1, 1, 1)$ & $(-1, 1, 1, 1)$ \\
$\mathbb{1}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\mathbb{1}$ & $\sigma_{x}\otimes\sigma_{z}$ & $(1, 0, 1, 0)$ & $(0, 1, 0, 1)$ & $(1, 0, -1, 0)$ & $(0, 1, 0, -1)$ \\
$\sigma_{z}\otimes\mathbb{1}$ & $\mathbb{1}\otimes\sigma_{x}$ & $\sigma_{z}\otimes\sigma_{x}$ & $(1, 1, 0, 0)$ & $(1, -1, 0, 0)$ & $(0, 0, 1, 1)$ & $(0, 0, 1, -1)$ \\
$\sigma_{z}\otimes\sigma_{z}$ & $\sigma_{x}\otimes\sigma_{x}$ & $\sigma_{y}\otimes\sigma_{y}$ & $(0, 1, 1, 0)$ & $(0, 1, -1, 0)$ & $(1, 0, 0, 1)$ & $(1, 0, 0, -1)$ \\
\end{tabular} 
\end{ruledtabular}
\end{table}
Since observables in equation~(\ref{eq:MerminSquare}) are not projections,
if we want to reformulate the above argument in the language of quantum
probability measures, we first need to find the common eigenbasis
of each row and column, and consider the projections to each eigenvectors.
Let $\mathcal{T}_{24}$ denote all eigenstates listed in table~\ref{table:commonBasis}.
The Kochen-Specker theorem could then be proved by showing there is
no function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $ satisfying
equation~(\ref{eq:Kochen-Specker-Rules}), where 
\begin{equation}
\events_{24}=\set{\sum_{i=1}^{N}\proj{\psi_{i}}}{\textrm{mutually orthogonal }\left\{ \ket{\psi_{i}}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{24}}
\end{equation}
which is a sub-event space defined in definition~\ref{def:sub-event-space}.
This kind of $v$ is actually a quantum cryptodeterministic measure.
Since a cryptodeterministic measure is a special case of real-valued
probability measure, by theorem~\ref{lemma:classical-probability-measures},
the quantum cryptodeterministic measure~$v$ exists if and only if
there exists a frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
which should at least satisfy
\begin{eqnarray}
1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)
\label{eq:Kernaghan-1}\end{eqnarray}
because of table~\ref{table:commonBasis}. $f$ should also satisfy
the following equations since the vectors in each equation form an
orthogonal basis~\cite{Kernaghan1994,peres1995quantum}:
\begin{eqnarray}
1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}
\label{eq:Kernaghan-2}\end{eqnarray}
In equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}, there
are odd number of equations, but each $f\left(\alpha_{0},\alpha_{1},\alpha_{2},\alpha_{3}\right)$
occurs twice. Therefore, there is no frame function~$f:\mathcal{T}_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2}.

@@

First, based on a Born rule probability measure, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
it is easy to construct a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
whose unique core element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$.
For example, when $\mathscr{I}$ is $\left\{ \imposs,\necess,\left[\frac{1}{4},\frac{1}{4}\right],\left[\frac{1}{2},\frac{1}{2}\right],\left[\frac{3}{4},\frac{3}{4}\right]\right\} $,
we have $\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events_{24}\rightarrow\mathscr{I}$
and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
where $\iota_{\infty}\left(x\right)=\left[x,x\right]$ and $\circ$
denote function composition. This provides an example that a well-behaved
quantum IVPM exists even if $\mathscr{I}$ is discrete. Well-behaved
quantum IVPMs happen when mapping to other kind of intervals. For
example, we can add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Let 
\begin{equation} 
\iota_1(x)=\begin{cases} 
\necess & \text{ if}x=1\text{ ;}\\ 
\imposs & \text{ if}x=0\text{ ;}\\ 
\unknown & \text{ otherwise.}
\end{cases}\label{eq:homomorphism-1} \end{equation}
We still have $\mathrm{core}\left(\iota_{1}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $.

@@

\begin{example}[Four-dimensional quantum real-valued probability
measure]\label{ex:four-dimensional-real-value}Consider the frame
function~$f:\mathcal{T}_{24}\rightarrow\left[0,1\right]$ again.
Apart from equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2},
$f$ should also satisfy the following equations: 
\begin{eqnarray}
1 = f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
1 = f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
1 = f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
1 = f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
1 = f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1)+f(1,1,-1,-1)\textrm{ ,}\\ 
1 = f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0)+f(1,1,1,-1)\textrm{ ,}\\ 
1 = f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1)+f(1,1,1,-1)\textrm{ ,}\\ 
1 = f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0)+f(1,1,1,1)\textrm{ ,}\\ 
1 = f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1)+f(1,1,1,1)\textrm{ .} 
\label{eq:non-Kernaghan}\end{eqnarray}
\qed\end{example}
